### 2016-11-23 intro.tex
Fishished Christine's revision suggestions

A wealth of studies have

The evolution of these superbubbles was studied in detail by \citet{MacLow1988}.
A key insight was that the hot bubble would evaporate the cold shell through
thermal conduction.  In a hot ionized plasma, electrons are able to penetrate
temperature gradients and deposit energy within cooler material.  This produces
a pressure gradient that establishes a mass flux against the temperature
gradient, evaporating the cold shell into the hot bubble.  This
evaporation means that a hot bubble with temperature $T$ and radius $R$ gains
mass at a rate of:
\begin{equation}
    \frac{{\rm d }M_b}{{\rm d}t} = \frac{16\pi\mu}{25k_B} CT^{5/2}R
\end{equation}
Where $C=6\times10^{-7}\;\rm{erg\;s^{-1}\;cm^{-1}\;K^{7/2}}$, and $\mu$ is the
mean molecular weight of the gas in the bubble.  As the cold, evaporated
material acts to cool the hot bubble, this makes the bubble's interior
temperature self-regulating: higher temperatures give higher mass flux, cooling
the bubble.

>>>>

The structure and evolution of superbubbles have been the subject of a great
deal of analytic study.  \citet{Castor1975} found that the time evolution of
superbubbles has a similarity solution, similar to the \citet{Sedov1959}
adiabatic blast wave solution: $R(t)=27n_0^{-1/5}L_{36}^{1/5}t_6^{3/5}\;\rm{pc}$
and $V(t)=16n_0^{-1/5}L_{36}^{1/5}t_6^{-2/5}\;\rm{km/s}$ , where $n_0$ is the
ambient density in $\rm{cm^{-3}}$, $L_{36}$ is the luminosity of the star
cluster in $10^{36}\;\rm{erg/s}$, and $t_6$ is the time in $10^6\;\rm{yr}$.  The
evolution of hot mass in the bubble, and the effects of cooling in the swept-up
shell, were examined in \citet{Weaver1977}.  A major result of this study was
the realization that thermal conduction between the hot bubble and cold shell
will result in an evaporative mass flux, pulling material into the hot bubble.
This evaporated mass will quickly dominate over the small amount of ejecta from
stellar winds.  The \citet{Weaver1977} results were extended to clustered SN by
\citet{MacLow1988}.  They calculated that the typical cooling time for the hot
bubble was $\sim15\;\rm{Myr}$, with a weak dependence on the total luminosity
and ambient density.  Before significant cooling can occur in the hot interior,
$27/77$ of the total feedback luminosity is lost too cooling of the swept-up
shell, which cools in $\sim10^4\;\rm{yr}$.  \citet{MacLow1988} also demonstrated
that, as superbubbles do not have surface tension, they are not depressurized by
cold clouds, and instead simply deform around them while continuing to expand.
\citet{Silich1996} studied the effects of an ISM permeated with cold clumps in
greater detail, finding that the general behaviour discussed in
\citet{MacLow1988} held even in the case of an inhomogeneous ISM.  Even with
$50\%$ of the ISM mass trapped in cold clouds (which penetrate the cold shell of
the superbbule), the total hot mass within the superbubble will only vary by $\sim20\%$.

A key insight in these studies was that hot bubbles would evaporate their cold
shell through thermal conduction.  In a hot ionized plasma, electrons are able
to penetrate temperature gradients and deposit energy within cooler material.
This produces a pressure gradient that establishes a mass flux against the
temperature gradient, evaporating the cold shell into the hot bubble.  This
evaporation means that a hot bubble with temperature $T$ and radius $R$ gains
mass at a rate of:
\begin{equation}
    \frac{{\rm d }M_b}{{\rm d}t} = \frac{16\pi\mu}{25k_B} CT^{5/2}R
\end{equation}
Where $C=6\times10^{-7}\;\rm{erg\;s^{-1}\;cm^{-1}\;K^{7/2}}$, and $\mu$ is the
mean molecular weight of the gas in the bubble.  As the cold, evaporated
material acts to cool the hot bubble, this makes the bubble's interior
temperature self-regulating: higher temperatures give higher mass flux, cooling
the bubble.
